Real Time Adaptive Shape Reconstruction for Asteroid Landing

### 2018-12-13 manuscript.tex
revisec sec 5

We consider two simulations about asteroids \num{52760} and Castalia.
The asteroids are assumed to constantly rotate about the \( \vc{f}_3 = \vc{e}_3\) axis according to the parameters given in~\cref{tab:dynamic_asteroids}.
Furthermore, the state of the asteroid, namely the rotation matrix \( R_A \), is assumed to be known based on ground measurements or previous data.
\begin{table}[htbp]
    \centering
    \begin{tabular}{lcc}
        \toprule
        Property & \num{4769} Castalia & (\num{52760}) \num{1998} \(\text{ML}_{14}\) \\
        \midrule
        Semi-major axes(\si{\kilo\meter}) & \( 0.8065 \times 0.4905 \times 0.413 \) & \( 1.1 \times 1.1 \times 1.1 \) \\
        Rotational Period (\si{\hour}) & \num{4.095} & \num{14.98} \\
        Density (\si{\gram\per\centi\meter^3}) & \num{2.1} & \num{2.1} \\
        Vertices & \num{2048}  & \num{8192} \\
        Faces & \num{4092} & \num{16320} \\
        \bottomrule
    \end{tabular}
    \caption{Asteroid properties for dynamic exploration~\label{tab:dynamic_asteroids}}
\end{table}
At the beginning of the simulation the spacecraft is assumed to lie on the inertial \( e_1 \) axis, i.e.\ \( x_0 = \begin{bmatrix} x_0 & 0 & 0 \end{bmatrix} \si{\kilo\meter} \).
In addition, at the initial state the spacecraft is orientated such that the \( b_1 \) axis is aligned with the inertial \( e_2 \) axis.
In other words the initial orientation is given by \( R_0 = \exp(\frac{\pi}{2} \hat{e}_3)\).
The shape reconstruction phase of the simulation is performed over \SI{15000}{\second}, over which time the spacecraft will take LIDAR measurements of the surface at \SI{1}{\hertz}.
Once the total uncertainty has been reduced sufficiently the spacecraft maneuvers to a ``home'' position aligned with the \( f_1 \) axis of the asteroid.

@@

The shape update approach presented is designed with autonomous operations in mind. 
It is based on an initial coarse shape estimate that is iteratively updated with range measurements of the surface.
Furthermore, the original mesh is uniformly distributed and as a result many small topological features such as rocks or small craters are not be captured by the shape model. 
However, these small features are critical for surface operations and safe landings.
In addition, it would be computationally prohibitive to have a uniformly high resolution mesh.
In this section, we extend the previous shape update approach to enable a much higher fidelity in a specific location.

@@

Additionally, we compute the distance, using~\cref{eq:geodesic_distance}, between the spacecraft state and each face of the asteroid. 
Finally, we also assign a random science value to the surface in the form of a two dimensional Gaussian.
Utilizing these metric, a landing site is chosen to minimize the surface cost given as
\begin{align}\label{eq:surface_cost}
    J_l =  J_{\text{distance}} - J_{\text{science}},
\end{align}
where the surface slope is considered a hard constraint such that any candidate landing site must satisfy \( \phi \leq \phi_m \).

\paragraph{Mesh Refinement}\label{sec:refinement}

Once a suitable landing site is selected, the surrounding area is isolated and refined by adding new vertices and faces in the specified area.
The goal of refinement, or more generally remeshing, is given a mesh ( or a portion of it), compute another mesh whose elements satisfy some quality metrics while suitably approximating the original mesh.
In this work, we utilize the isotropic remeshing algorithm implemented in the Computational Geometry and Algorithms Library (CGAL).
This algorithm uses an iterative method which repeatedly splits long edges, collapses short edges, and relocates vertices until all edges are approximately the desired target edge length.
% TODO Think about adding PMP 6.12 image here

@@

In order to demonstrate the multi resolution surface refinement we require a true shape model that contains small scale surface features.
In this dissertation, we utilize the true radar shape model of asteroid 4769 Castalia.
However, the shape model is not highly detailed as it does not contain small craters or surface features.
In order to apply the landing refinement process we augment a small portion of the mesh with some additional features and utilize the mesh update scheme shown previously to update the surface.
The augmented model of Castalia is shown in~\cref{fig:castalia_refinement}.
\Cref{fig:castalia_refinement} shows that the increased resolution is required in order to reconstruct these small surface details.

\section{Numerical Examples}\label{sec:reconstruction_examples}

% TODO Add more plots from dissertation. All the uncertainty and volume plots
% TODO Show examples with the other asteroids
% TODO Mention that the software to do this is available online?
\paragraph{Castalia Landing Site Selection}

@@

\paragraph{Castalia Landing Site Refinement}
One key benefit of an in-situ spacecraft is the ability to measure surface features at a much higher resolution than is possible from the ground. 
This detail provides a much higher fidelity data source than ground based measurements. 
In order to emulate this in the simulation we augment the shape model of Castalia with several small craters and outcroppings as shown in~\cref{fig:castalia_refinement}.
However, these small features would be difficult to capture with the current low resolution shape model of approximately \num{4000} faces.
The lower number of faces is useful for the evaluation of the polyhedron potential model, it is not ideal for the capture of minute surface features. 
As a result, we utilize the isotropic remeshing operation described previously to selectively increase the fidelity in the region about the desired landing site.
\Cref{fig:castalia_refine_density} shows that the vertex density increases by approximately an order of magnitude in region immediately surround the landing site.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/density.pdf}}%
    \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/land/density.pdf}}
    \caption{Vertex density before and after refinement at asteroid Castalia\label{fig:castalia_refine_density}}
\end{figure}

@@

@@

This paper developed a Bayesian update scheme to reconstruct the shape of a small body from range measurements. 
The approach allows for a local update operation that is able to reconstruct the shape in real time. 
This is in contrast to standard shape reconstruction algorithms which operate over the entire surface and require signification computational resources.
Next, an optimal guidance scheme is derived which determines the desired state to best update the shape estimate. 
This allows for a spacecraft to autonomously maneuver and reconstruct the shape of a small body without operator intervention.
% Finally, a mixed resolution shape representation is presented to allow for an increased fidelity in a specific region of the asteroid.
% This allows for a much greater shape accuracy in a local area while avoiding the computational costs associated with a uniformly high resolution mesh.
Several numerical examples were presented which demonstrates the approach on a number of real asteroids.

\section*{Appendix}

An Appendix, if needed, appears \textbf{before} research funding information and other acknowledgments.

\section*{Funding Sources}

Sponsorship information and acknowledgments of financial support should be included here. \textbf{Authors are responsible for accurately reporting funding data relevant to their research.} Please confirm that you have correctly entered \textbf{all sources} of funding and grant/award numbers \textbf{for all authors} in this section of your article. You will also be asked to select the appropriate funding organization from a drop-down menu in ScholarOne when you submit your manuscript. Be careful to choose the correct funder name, as organization names can be similar, and also be mindful to select sub-organizations within the registry hierarchy that are the actual funding sources, as appropriate, rather than choosing the name of the parent organization. Information provided in your manuscript must match the funding data entered in ScholarOne.

>>>>

The asteroids are assumed to constantly rotate about the \( \vc{f}_3 = \vc{e}_3\) axis according to the parameters given in~\cref{tab:dynamic_asteroids}.
Furthermore, the state of the asteroid, namely the rotation matrix \( R_A \), is assumed to be known based on ground measurements or previous data.
\begin{table}[htbp]
    \centering
    \begin{tabular}{lcc}
        \toprule
        Property & \num{4769} Castalia & (\num{52760}) \num{1998} \(\text{ML}_{14}\) \\
        \midrule
        Semi-major axes(\si{\kilo\meter}) & \( 0.8065 \times 0.4905 \times 0.413 \) & \( 1.1 \times 1.1 \times 1.1 \) \\
        Rotational Period (\si{\hour}) & \num{4.095} & \num{14.98} \\
        Density (\si{\gram\per\centi\meter^3}) & \num{2.1} & \num{2.1} \\
        Vertices & \num{2048}  & \num{8192} \\
        Faces & \num{4092} & \num{16320} \\
        \bottomrule
    \end{tabular}
    \caption{Asteroid properties for dynamic exploration~\label{tab:dynamic_asteroids}}
\end{table}
At the beginning of the simulation the spacecraft is assumed to lie on the inertial \( e_1 \) axis, i.e.\ \( x_0 = \begin{bmatrix} x_0 & 0 & 0 \end{bmatrix} \si{\kilo\meter} \).
In addition, at the initial state the spacecraft is orientated such that the \( b_1 \) axis is aligned with the inertial \( e_2 \) axis.
In other words the initial orientation is given by \( R_0 = \exp(\frac{\pi}{2} \hat{e}_3)\).
The shape reconstruction phase of the simulation is performed over \SI{15000}{\second}, over which time the spacecraft will take LIDAR measurements of the surface at \SI{1}{\hertz}.
Once the total uncertainty has been reduced sufficiently the spacecraft maneuvers to a ``home'' position aligned with the \( f_1 \) axis of the asteroid.

@@

In this section, we consider a scenario of autonomous landing on the surface of asteroid, once its shape is constructed as described above.
The shape reconstruction scheme is based on an initial coarse shape estimate that is iteratively updated with range measurements of the surface.
Consequently, the original mesh is uniformly distributed with a relatively large mesh size and many small topological features such as rocks or small craters may not be captured accurately.
However, these small features are critical for surface operations and safe landings.
In addition, it would be computationally prohibitive to have a uniformly high resolution mesh.
In this section, we extend the previous shape update approach to enable a much higher fidelity in a specific location.

\subsection{Landing Site Determination}

@@

Additionally, we compute the distance, using~\cref{eq:geodesic_distance}, between the spacecraft state and each face of the asteroid. 
Finally, we also assign a random science value to the surface in the form of a two dimensional Gaussian.
This can be modified depending on the specific objective of the mission.

Utilizing these metric, a landing site is chosen to minimize the surface cost given as
\begin{align}\label{eq:surface_cost}
    J_l =  J_{\text{distance}} - J_{\text{science}},
\end{align}
subject to a hard inequality constraint requiring that the surface slope is less than a threshold, i.e., \( \phi \leq \phi_m \).

\todo{rewrite the above equation as a function of a candidate landing site location; we also need to describe how many points are considered for minimization; is it just the set of vertices}

\subsection{High-Resolution Mapping}\label{sec:refinement}

Once a suitable landing site is selected, the surrounding area is isolated and refined by adding new vertices and faces in the specified area.
The goal of refinement, or more generally remeshing, is given a mesh ( or a portion of it), compute another mesh whose elements satisfy some quality metrics while suitably approximating the original mesh.
In this work, we utilize the isotropic remeshing algorithm implemented in the Computational Geometry and Algorithms Library (CGAL).
\todo{add reference to CGAL}
This algorithm uses an iterative method which repeatedly splits long edges, collapses short edges, and relocates vertices until all edges are approximately the desired target edge length.
% TODO Think about adding PMP 6.12 image here

@@

Once the area around the landing site is remeshed, the preceding shape reconstruction scheme is applied to those area to develop a high-fidelity topological map.

\subsection{Numerical Example}

The proposed schemes for landing site selection and refinement are applied to Castalia.

%\section{Numerical Examples}\label{sec:reconstruction_examples}

% TODO Add more plots from dissertation. All the uncertainty and volume plots
% TODO Show examples with the other asteroids
% TODO Mention that the software to do this is available online?

\paragraph{Castalia Landing Site Selection}

@@

\paragraph{Castalia Landing Site Refinement}

%In order to demonstrate the multi resolution surface refinement we require a true shape model that contains small scale surface features.
%Here, we utilize the true radar shape model of asteroid 4769 Castalia.
%However, the shape model is not highly detailed as it does not contain small craters or surface features.
%In order to apply the landing refinement process we augment a small portion of the mesh with some additional features and utilize the mesh update scheme shown previously to update the surface.
%The augmented model of Castalia is shown in~\cref{fig:castalia_refinement}.
%\Cref{fig:castalia_refinement} shows that the increased resolution is required in order to reconstruct these small surface details.

One key benefit of an in-situ spacecraft is the ability to measure surface features at a much higher resolution than is possible from the ground. 
This detail provides a much higher fidelity data source than ground based measurements. 
In order to emulate this in the simulation we augment the shape model of Castalia with several small craters and outcroppings as shown in~\cref{fig:castalia_refinement}.
However, these small features would be difficult to capture with the current low resolution shape model of approximately \num{4000} faces.
The lower number of faces is useful for the evaluation of the polyhedron potential model, it is not ideal for the capture of minute surface features. 
As a result, we utilize the isotropic remeshing operation described previously to selectively increase the fidelity in the region about the desired landing site.

\Cref{fig:castalia_refine_density} shows that the vertex density increases by approximately an order of magnitude in region immediately surround the landing site.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/density.pdf}}%
    \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/land/density.pdf}}
    \caption{Vertex density before and after refinement at asteroid Castalia\label{fig:castalia_refine_density}}
\end{figure}

@@

\todo{as the nonlinear controller is added, we may want to add more plots for tracking errors; we can add a link to videos}

@@

This paper developed a Bayesian update scheme to reconstruct the shape of a small body from range measurements. 
The approach allows for a local update operation that is able to reconstruct the shape in real time. 
This is in contrast to standard shape reconstruction algorithms which operate over the entire surface and require signification computational resources.
Next, an optimal guidance scheme is derived which determines the desired state to best update the shape estimate. 
Finally, a mixed resolution shape representation is presented to allow for an increased fidelity in a specific region of the asteroid.
This allows for a much greater shape accuracy in a local area while avoiding the computational costs associated with a uniformly high resolution mesh.
This allows for a spacecraft to autonomously maneuver and reconstruct the shape of a small body without operator intervention.
Several numerical examples were presented which demonstrates the approach on a number of real asteroids.

Throughout this paper, it is considered that the position of the spacecraft relative the asteroid is available. 
Future works include integrating a localization technique with the proposed shape reconstruction scheme such that the relative location and the shape model are estimated simultaneously.

%\section*{Appendix}

%An Appendix, if needed, appears \textbf{before} research funding information and other acknowledgments.

%\section*{Funding Sources}

%Sponsorship information and acknowledgments of financial support should be included here. \textbf{Authors are responsible for accurately reporting funding data relevant to their research.} Please confirm that you have correctly entered \textbf{all sources} of funding and grant/award numbers \textbf{for all authors} in this section of your article. You will also be asked to select the appropriate funding organization from a drop-down menu in ScholarOne when you submit your manuscript. Be careful to choose the correct funder name, as organization names can be similar, and also be mindful to select sub-organizations within the registry hierarchy that are the actual funding sources, as appropriate, rather than choosing the name of the parent organization. Information provided in your manuscript must match the funding data entered in ScholarOne.
